% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hannah Estes}

\basicInfo{
  \email{hannahmestes@gmail.com} \textperiodcentered\ 
  \phone{(+1) 480-298-5039} \textperiodcentered\ 
  \linkedin[esteshannah]{https://www.linkedin.com/in/esteshannah/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Texas Tech University (TTU)}, Lubbock, Texas}{2016 -- 2019}
\textit{Bachelor's Degree} in Computer Science

\section{\faUsers\ Experience}
\datedsubsection{\textbf{State Farm Insurance} Tempe, Arizona}{2015 -- Present}
\role{iOS Developer}{Sundial Labs}{July 2020 -- Present}
Develop and maintain the iOS application for Sundial, a senior care platform created by State Farm.
\begin{itemize}
  \item Migrated application dependecy management systems in order to comply with new security policies.
  \item Improved accessibility and created an adapted version of the application for seniors.
  \item Awarded prize for 'Most Business Value' in enterprise-wide hackathon for developing a VR collaboration proof of concept.
\end{itemize}

\role{Software Developer}{RED Labs}{January 2020 -- July 2020}
Designed user interfaces and system architecture for a pilot policy management system.
\begin{itemize}
  \item Developed several prototypes for user testing using Sketch.
  \item Collaborated with underwriters and actuaries to devlop innovative strategies using telematics.
  \item Designed architecture for a policy sale and maintenance using a blend of cloud and on premises solutions. 
  \item Served as an advisor for the intern public speaking program, coaching 6 interns for 8 weeks.
\end{itemize}

\role{Software Development Intern}{RED Labs}{Summer 2018 -- 2019}
Developed virtual reality training applications and conducted experiments on their efficacy.
\begin{itemize}
  \item Developed virtual reality applications for Windows Mixed Reality platform using Unity.
  \item Designed and developed a dashboard for analyzing usage metrics collected during experiments.
  \item Participated in a 4-week Agile Dojo while a member of the VR development team.
  \item Semifinalist in public speaking competition, and later served as assistant advisor for the program.
\end{itemize}

\role{Software Development Intern}{Enterprise Technology}{Summer 2015 -- 2017}
Developed a variety of software solutions to address critical business needs.
\begin{itemize}
  \item Collaborated with a team of interns to develop a dashboard for tracking key developer metrics using Spring Boot, Angular, and Django.
  \item Developed and maintained hundreds of automated integration tests for customer login and authentication using Cucumber.
  \item Enhanced critical features of policy creation tools in an application rewrite.
\end{itemize}

\datedsubsection{\textbf{Caprock Custom Applications} Lubbock, Texas}{September 2018 -- May 2019}
\role{Intern}
Brief introduction: Developed mobile and web applications for a variety of local clients.
\begin{itemize}
  \item Developed and maintained hybrid mobile applications for Android and iOS using Ionic with Angular.
  \item Designed and developed a system that aids nurses and physicians in diagnosing common conditions in nursing home residents using Express and MySQL.
  \item Built sales, social, and information applications in a startup environment.
\end{itemize}

\datedsubsection{\textbf{The Choice VR}}{January 2020 -- Present}
\role{Developer}
A VR documentary about reproductive rights. https://www.thechoice-vr.com/
\begin{itemize}
  \item Collaborate with a group of filmmakers, artists, and writers to develop an immersive interview experience.
  \item Designed and implemented features that enable an interactive interview experience.
  \item Developed using Unity with Bolt.
  \item Targeting submission to several film festivals in 2021.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills and Specialties}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C#, JavaScript, Swift
  \item Frameworks: Angular, Ionic, Express
  \item Worth Mentioning: Well versed in Git, Agile/SAFe priciples, and Scrum/Kanban practices.
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
